Type Error Telemetry at Scale

### 2023-09-24 programming23/paper.tex
rename error labels: shorten, put ExtraInfo next to GenError where it belongs

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}
\newcommand{\percentile}[1]{{#1}th~percentile}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\stddev}[1]{[#1\textsc{k}]}
\newcommand{\gcell}[1]{\cellcolor{green!20}#1}
\newcommand{\ycell}[1]{\cellcolor{yellow!18}#1}
\newcommand{\ocell}[1]{\cellcolor{orange!29}#1}
\newcommand{\rcell}[1]{\cellcolor{red!30}$\!\!$#1$\!\!$}
\newcommand{\gbox}[1]{\colorbox{green!20}{#1}}
\newcommand{\ybox}[1]{\colorbox{yellow!18}{#1\vphantom{Ap}}}
\newcommand{\obox}[1]{\colorbox{orange!29}{#1\vphantom{Ap}}}
\newcommand{\rbox}[1]{\colorbox{red!30}{#1\vphantom{Ap}}}
\newcommand{\tefsfont}[1]{\textsc{#1}}
\newcommand{\tekey}{\tefsfont{te}}
\newcommand{\fskey}{\tefsfont{fs}}
\newcommand{\QALAN}{\FILL{} Alan:}

@@

    \code{CountMismatch} & Arity mismatch for a function \\
    \code{IncorrectGenericParameterCount} & Arity mismatch for a generic type \\
    \code{UnknownProperty} & Referenced an invalid field or method  \\
    \code{OnlyTablesCanHaveMethods} & Tried to attach a method to a non-table \\
    \code{CannotCallNonFunction} & Called a value that is not a function \\
    \code{TypesAreUnrelated} & Failed to cast, unify, or check subtyping \\
    \code{TypeMismatch} & Generic label for other type errors \\
    \code{GenericError}
    & Generic label for other non-type errors, such as\\
    & \hbox{}~~looping over an unordered table
    %% attempting to extend a type that does not describe a class
    %% attempting to iterate over a table without a clear order

%    \code{ExtraInformation} & Follow-on error that provides additional information for an error at the same source location. \\
%    UnknownSymbol &  \\
%    NotATable &  \\
%    CannotExtendTable &  \\
%    DuplicateTypeDefinition &  \\
%    FunctionDoesNotTakeSelf &  \\
%    FunctionRequiresSelf &  \\
%    OccursCheckFailed &  \\
%    UnknownRequire &  \\
%    UnknownPropButFoundLikeProp &  \\
%    InternalError &  \\
%    DeprecatedApiUsed &  \\
%    ModuleHasCyclicDependency &  \\
%    IllegalRequire &  \\
%    FunctionExitsWithoutReturning &  \\
%    DuplicateGenericParameter &  \\
%    CannotInferBinaryOperation &  \\
%    MissingProperties &  \\
%    SwappedGenericTypeParameter &  \\
%    OptionalValueAccess &  \\
%    MissingUnionProperty &  \\
%    NormalizationTooComplex &  \\
%    TypePackMismatch &  \\
%    DynamicPropertyLookupOnClassesUnsafe &  \\)
  \end{tabular}
\end{table}

@@

\begin{figure}
  \begin{tabular}{|l|l|l|l|l|l|l|l|l|}\midrule
    meta & size & te count & fs count & te 0 & te 1 & te 2 \ldots
    \\\midrule
  \end{tabular}
  \caption{Struture of a telemetry record}
  \label{f:tdata}
\end{figure}

@@

\begin{table}[t]
  \caption{Number of records that add, keep, or drop (remove) specific type errors from their edit range.}
  \label{t:type-error-survival}
  \begin{tabular}{lr@{}r@{}rr@{}r@{}rr@{}r@{}r}
    & \zerowidth{\mnocheck{}} & & & \zerowidth{\mnonstrict{}} & & & \zerowidth{\mstrict{}} & & \\
    & \rbox{Add} & \ybox{Keep} & \gbox{Drop} & \rbox{Add} & \ybox{Keep} & \gbox{Drop} & \rbox{Add} & \ybox{Keep} & \gbox{Drop} \\\midrule
    \code{CannotCallNonFunction} & {0} & {0} & {0} & {17} & {4} & {20} & {1} & {0} & {1} \\
    \code{CannotExtendTable} & {0} & {0} & {0} & {7} & {9} & {10} & {0} & {0} & {1} \\
    \code{CannotInferBinaryOperation} & {0} & {0} & {0} & {1} & {2} & {1} & {7} & {6} & {9} \\
    \code{CountMismatch} & {0} & {0} & {0} & {223} & {48} & {269} & {12} & {2} & {17} \\
    \code{DuplicateTypeDefinition} & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {0} \\
    \code{ExtraInformation} & {0} & {0} & {0} & {48} & {7} & {39} & {2} & {0} & {1} \\
    \code{FunctionDoesNotTakeSelf} & {0} & {0} & {0} & {4} & {6} & {5} & {0} & {0} & {0} \\
    \code{FunctionExitsWithoutReturning} & {0} & {0} & {0} & {9} & {3} & {6} & {11} & {5} & {8} \\
    \code{GenericError} & {0} & {0} & {0} & {206} & {52} & {203} & {8} & {1} & {9} \\
    \code{IllegalRequire} & {0} & {0} & {0} & {16} & {3} & {33} & {0} & {0} & {2} \\
    \code{IncorrectGenericParameterCount} & {0} & {0} & {0} & {0} & {0} & {0} & {1} & {0} & {1} \\
    \code{MissingProperties} & {0} & {0} & {0} & {11} & {3} & {11} & {6} & {4} & {6} \\
    \code{MissingUnionProperty} & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
    \code{ModuleHasCyclicDependency} & {0} & {0} & {0} & {20} & {9} & {15} & {0} & {0} & {1} \\
    \code{NotATable} & {0} & {0} & {0} & {7} & {2} & {8} & {2} & {0} & {1} \\
    \code{OccursCheckFailed} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {1} \\
    \code{OnlyTablesCanHaveMethods} & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
    \code{OptionalValueAccess} & {0} & {0} & {0} & {40} & {52} & {27} & {6} & {2} & {7} \\
    \code{SyntaxError} & {8349} & {314} & {19220} & {983} & {46} & {2658} & {16} & {0} & {71} \\
    \code{TypeMismatch} & {0} & {0} & {0} & {159} & {62} & {129} & {21} & {10} & {28} \\
    \code{TypesAreUnrelated} & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {1} \\
    \code{UnknownPropButFoundLikeProp} & {0} & {0} & {0} & {26} & {18} & {21} & {1} & {0} & {1} \\
    \code{UnknownProperty} & {0} & {0} & {0} & {347} & {180} & {385} & {19} & {19} & {35} \\
    \code{UnknownRequire} & {0} & {0} & {0} & {91} & {39} & {85} & {12} & {3} & {4} \\
    \code{UnknownSymbol} & {0} & {0} & {0} & {2348} & {496} & {2973} & {49} & {19} & {55}
  \end{tabular}

@@

  \item
    (NOTE may want to save relative popularity for next section.)
    Some errors occur more often in \mnonstrict{} than \mstrict{}:
    \code{CannotCallNonFunction},
    \code{CannotExtendTable},
    \code{ExtraInformation},
    \code{FunctionDoesNotTakeSelf},
    \code{IllegalRequire},
    \code{ModuleHasCyclicDependency},
    \code{OptionalValueAccess},
    \code{UnknownPropButFoundLikeProp}.
    \QALAN{} are any of these surprising, or expected from the bigger number of
    \mnonstrict{} records?

  \item
    A few errors are more common in \mstrict{} than \mnonstrict{}:
    \code{CannotInferBinaryOperation},
    \code{FunctionExitsWithoutReturning},
    \code{IncorrectGenericParameterCount}.
    \FILL{} so what.

@@

\begin{table}[t]\centering
  %% NOTE: popularity looks similar when [over all records] vs. [restricted to module switch records]
  \caption{Type error popularity for \mnonstrict{} and \mstrict{} modes.
    All of the type errors in \mnocheck{} mode are \code{SyntaxError}s.}
  \label{t:type-error-count}
  \begin{tabular}{ll}
    \mnonstrict{} & \mstrict{} \\
    \begin{tabular}[t]{l@{~}r}
      \code{UnknownSymbol} & \pct{62.13} \\
      \code{SyntaxError} & \pct{15.42} \\
      \code{UnknownProperty} & \pct{8.28} \\
      \code{UnknownRequire} & \pct{3.13} \\
      \code{TypeMismatch} & \pct{2.44} \\
      \code{CountMismatch} & \pct{2.26} \\
      \code{OptionalValueAccess} & \pct{2.07} \\
      \code{GenericError} & \pct{2.06} \\
      \code{UnknownPropButFoundLikeProp} & \pct{0.44} \\
      \code{CannotExtendTable} & \pct{0.42} \\
      \code{ExtraInformation} & \pct{0.32} \\
      \code{ModuleHasCyclicDependency} & \pct{0.23} \\
      \code{IllegalRequire} & \pct{0.20} \\
      \code{NotATable} & \pct{0.15} \\
      \code{CannotCallNonFunction} & \pct{0.15} \\
      \code{MissingProperties} & \pct{0.09} \\
      \code{FunctionExitsWithoutReturning} & \pct{0.07} \\
      \code{FunctionDoesNotTakeSelf} & \pct{0.07} \\
      \code{MissingUnionProperty} & \pct{0.02} \\
      \code{CannotInferBinaryOperation} & \pct{0.02} \\
      \code{OnlyTablesCanHaveMethods} & \pct{0.01} \\
      \code{DuplicateTypeDefinition} & {<\pct{0.01}} \\
      \code{TypesAreUnrelated} & {<\pct{0.01}} \\
    \end{tabular}
        &
    \begin{tabular}[t]{l@{~}r}
      \code{UnknownSymbol} & \pct{23.97} \\
      \code{TypeMismatch} & \pct{20.46} \\
      \code{UnknownProperty} & \pct{18.88} \\
      \code{SyntaxError} & \pct{9.31} \\
      \code{CannotInferBinaryOperation} & \pct{6.94} \\
      \code{MissingProperties} & \pct{4.04} \\
      \code{CountMismatch} & \pct{2.99} \\
      \code{OptionalValueAccess} & \pct{2.99} \\
      \code{FunctionExitsWithoutReturning} & \pct{2.99} \\
      \code{UnknownRequire} & \pct{2.37} \\
      \code{GenericError} & \pct{2.28} \\
      \code{NotATable} & \pct{1.32} \\
      \code{ExtraInformation} & \pct{0.35} \\
      \code{UnknownPropButFoundLikeProp} & \pct{0.26} \\
      \code{IncorrectGenericParameterCount} & \pct{0.18} \\
      \code{CannotCallNonFunction} & \pct{0.18} \\
      \code{IllegalRequire} & \pct{0.18} \\
      \code{ModuleHasCyclicDependency} & \pct{0.09} \\
      \code{CannotExtendTable} & \pct{0.09} \\
      \code{OccursCheckFailed} & \pct{0.09} \\
      \code{TypesAreUnrelated} & \pct{0.09} \\
    \end{tabular}
  \end{tabular}
\end{table}

@@

  \item
    Two errors that appear in the \mstrict{} records
    never appear in \mnonstrict{}: \code{OccursCheckFailed} and \code{IncorrectGenericParameterCount}.
    We attribute these to more advanced uses of types in \mstrict{} mode.

>>>>

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}
\newcommand{\percentile}[1]{{#1}th~percentile}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\nK}[1]{#1\textsc{k}}
\newcommand{\stddev}[1]{[\nK{#1}]}
\newcommand{\gcell}[1]{\cellcolor{green!20}#1}
\newcommand{\ycell}[1]{\cellcolor{yellow!18}#1}
\newcommand{\ocell}[1]{\cellcolor{orange!29}#1}
\newcommand{\rcell}[1]{\cellcolor{red!30}$\!\!$#1$\!\!$}
\newcommand{\gbox}[1]{\colorbox{green!20}{#1}}
\newcommand{\ybox}[1]{\colorbox{yellow!18}{#1\vphantom{Ap}}}
\newcommand{\obox}[1]{\colorbox{orange!29}{#1\vphantom{Ap}}}
\newcommand{\rbox}[1]{\colorbox{red!30}{#1\vphantom{Ap}}}
\newcommand{\tefsfont}[1]{\textsc{#1}}
\newcommand{\tekey}{\tefsfont{te}}
\newcommand{\fskey}{\tefsfont{fs}}
\newcommand{\QALAN}{\FILL{} Alan:}

@@

    \code{CountMismatch} & Arity mismatch for a function \\
    \code{IncorrectGenericParamCount} & Arity mismatch for a generic type \\
    \code{UnknownProperty} & Referenced an invalid field or method  \\
    \code{OnlyTablesCanHaveMethods} & Tried to attach a method to a non-table \\
    \code{CannotCallNonFunction} & Called a value that is not a function \\
    \code{TypesAreUnrelated} & Failed to cast, unify, or check subtyping \\
    \code{TypeMismatch} & Generic label for other type errors \\
    \code{GenericError}
    & Generic label for other non-type errors, such as\\
    & \hbox{}~~looping over an unordered table
    %% attempting to extend a type that does not describe a class
    %% attempting to iterate over a table without a clear order

%    \code{ExtraInformation} & Follow-on error that provides additional information for an error at the same source location. \\
%    UnknownSymbol &  \\
%    NotATable &  \\
%    CannotExtendTable &  \\
%    DuplicateTypeDefinition &  \\
%    FunctionDoesNotTakeSelf &  \\
%    FunctionRequiresSelf &  \\
%    OccursCheckFailed &  \\
%    UnknownRequire &  \\
%    UnknownPropButGotLikeProp &  \\
%    InternalError &  \\
%    DeprecatedApiUsed &  \\
%    ModuleHasCyclicDependency &  \\
%    IllegalRequire &  \\
%    FunctionExitsWithoutReturn &  \\
%    DuplicateGenericParameter &  \\
%    CannotInferBinaryOperation &  \\
%    MissingProperties &  \\
%    SwappedGenericTypeParameter &  \\
%    OptionalValueAccess &  \\
%    MissingUnionProperty &  \\
%    NormalizationTooComplex &  \\
%    TypePackMismatch &  \\
%    DynamicPropertyLookupOnClassesUnsafe &  \\)
  \end{tabular}
\end{table}

@@

\begin{figure}
  \fbox{
  }
  \begin{tabular}{|l|l|l|l|l|l|l|l|l|}\midrule
    meta & size & te count & fs count & te 0 & te 1 & te 2 \ldots
    \\\midrule
  \end{tabular}
  \caption{Struture of a telemetry record}
  \label{f:tdata}
\end{figure}

@@

\begin{table}[t]
  \caption{Number of telemetry records that add, keep, or drop (remove) specific type errors from their edit range.}
  \label{t:type-error-survival}
  \begin{tabular}{l@{}r@{}r@{}rr@{}r@{}rr@{}r@{}r}
    & \zerowidth{\mnocheck{}} & & & \zerowidth{\mnonstrict{}} & & & \zerowidth{\mstrict{}} & & \\
    & \rbox{Add} & \ybox{Keep} & \gbox{Drop} & \rbox{Add} & \ybox{Keep} & \gbox{Drop} & \rbox{Add} & \ybox{Keep} & \gbox{Drop} \\\midrule
    \code{CannotCallNonFunction} & {0} & {0} & {0} & {17} & {4} & {20} & {1} & {0} & {1} \\
    \code{CannotExtendTable} & {0} & {0} & {0} & {7} & {9} & {10} & {0} & {0} & {1} \\
    \code{CannotInferBinaryOperation} & {0} & {0} & {0} & {1} & {2} & {1} & {7} & {6} & {9} \\
    \code{CountMismatch} & {0} & {0} & {0} & {223} & {48} & {269} & {12} & {2} & {17} \\
    \code{DuplicateTypeDefinition} & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {0} \\
    \code{FunctionDoesNotTakeSelf} & {0} & {0} & {0} & {4} & {6} & {5} & {0} & {0} & {0} \\
    \code{FunctionExitsWithoutReturn} & {0} & {0} & {0} & {9} & {3} & {6} & {11} & {5} & {8} \\
    \code{GenericError} & {0} & {0} & {0} & {206} & {52} & {203} & {8} & {1} & {9} \\
    \code{GenericExtraInformation} & {0} & {0} & {0} & {48} & {7} & {39} & {2} & {0} & {1} \\
    \code{IllegalRequire} & {0} & {0} & {0} & {16} & {3} & {33} & {0} & {0} & {2} \\
    \code{IncorrectGenericParamCount} & {0} & {0} & {0} & {0} & {0} & {0} & {1} & {0} & {1} \\
    \code{MissingProperties} & {0} & {0} & {0} & {11} & {3} & {11} & {6} & {4} & {6} \\
    \code{MissingUnionProperty} & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
    \code{ModuleHasCyclicDependency} & {0} & {0} & {0} & {20} & {9} & {15} & {0} & {0} & {1} \\
    \code{NotATable} & {0} & {0} & {0} & {7} & {2} & {8} & {2} & {0} & {1} \\
    \code{OccursCheckFailed} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {1} \\
    \code{OnlyTablesCanHaveMethods} & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
    \code{OptionalValueAccess} & {0} & {0} & {0} & {40} & {52} & {27} & {6} & {2} & {7} \\
    \code{SyntaxError} & {8349} & {314} & {19220} & {983} & {46} & {2658} & {16} & {0} & {71} \\
    \code{TypeMismatch} & {0} & {0} & {0} & {159} & {62} & {129} & {21} & {10} & {28} \\
    \code{TypesAreUnrelated} & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {1} \\
    \code{UnknownPropButGotLikeProp} & {0} & {0} & {0} & {26} & {18} & {21} & {1} & {0} & {1} \\
    \code{UnknownProperty} & {0} & {0} & {0} & {347} & {180} & {385} & {19} & {19} & {35} \\
    \code{UnknownRequire} & {0} & {0} & {0} & {91} & {39} & {85} & {12} & {3} & {4} \\
    \code{UnknownSymbol} & {0} & {0} & {0} & {2348} & {496} & {2973} & {49} & {19} & {55}
  \end{tabular}

@@

  \item
    (NOTE may want to save relative popularity for next section.)
    Some errors occur more often in \mnonstrict{} than \mstrict{}:
    \code{CannotCallNonFunction},
    \code{CannotExtendTable},
    \code{GenericExtraInformation},
    \code{FunctionDoesNotTakeSelf},
    \code{IllegalRequire},
    \code{ModuleHasCyclicDependency},
    \code{OptionalValueAccess},
    \code{UnknownPropButGotLikeProp}.
    \QALAN{} are any of these surprising, or expected from the bigger number of
    \mnonstrict{} records?

  \item
    A few errors are more common in \mstrict{} than \mnonstrict{}:
    \code{CannotInferBinaryOperation},
    \code{FunctionExitsWithoutReturn},
    \code{IncorrectGenericParamCount}.
    \FILL{} so what.

@@

\begin{table}[t]\centering
  %% NOTE: popularity looks similar when [over all records] vs. [restricted to module switch records]
  \caption{Type error popularity for \mnonstrict{} and \mstrict{} modes.
    All of the type errors in \mnocheck{} mode are \code{SyntaxError}s.}
  \label{t:type-error-count}
  \begin{tabular}{ll}
    \mnonstrict{} & \mstrict{} \\
    \begin{tabular}[t]{l@{~}r}
      \code{UnknownSymbol} & \pct{62.13} \\
      \code{SyntaxError} & \pct{15.42} \\
      \code{UnknownProperty} & \pct{8.28} \\
      \code{UnknownRequire} & \pct{3.13} \\
      \code{TypeMismatch} & \pct{2.44} \\
      \code{CountMismatch} & \pct{2.26} \\
      \code{OptionalValueAccess} & \pct{2.07} \\
      \code{GenericError} & \pct{2.06} \\
      \code{UnknownPropButGotLikeProp} & \pct{0.44} \\
      \code{CannotExtendTable} & \pct{0.42} \\
      \code{GenericExtraInformation} & \pct{0.32} \\
      \code{ModuleHasCyclicDependency} & \pct{0.23} \\
      \code{IllegalRequire} & \pct{0.20} \\
      \code{NotATable} & \pct{0.15} \\
      \code{CannotCallNonFunction} & \pct{0.15} \\
      \code{MissingProperties} & \pct{0.09} \\
      \code{FunctionExitsWithoutReturn} & \pct{0.07} \\
      \code{FunctionDoesNotTakeSelf} & \pct{0.07} \\
      \code{MissingUnionProperty} & \pct{0.02} \\
      \code{CannotInferBinaryOperation} & \pct{0.02} \\
      \code{OnlyTablesCanHaveMethods} & \pct{0.01} \\
      \code{DuplicateTypeDefinition} & {<\pct{0.01}} \\
      \code{TypesAreUnrelated} & {<\pct{0.01}} \\
    \end{tabular}
        &
    \begin{tabular}[t]{l@{~}r}
      \code{UnknownSymbol} & \pct{23.97} \\
      \code{TypeMismatch} & \pct{20.46} \\
      \code{UnknownProperty} & \pct{18.88} \\
      \code{SyntaxError} & \pct{9.31} \\
      \code{CannotInferBinaryOperation} & \pct{6.94} \\
      \code{MissingProperties} & \pct{4.04} \\
      \code{CountMismatch} & \pct{2.99} \\
      \code{OptionalValueAccess} & \pct{2.99} \\
      \code{FunctionExitsWithoutReturn} & \pct{2.99} \\
      \code{UnknownRequire} & \pct{2.37} \\
      \code{GenericError} & \pct{2.28} \\
      \code{NotATable} & \pct{1.32} \\
      \code{GenericExtraInformation} & \pct{0.35} \\
      \code{UnknownPropButGotLikeProp} & \pct{0.26} \\
      \code{IncorrectGenericParamCount} & \pct{0.18} \\
      \code{CannotCallNonFunction} & \pct{0.18} \\
      \code{IllegalRequire} & \pct{0.18} \\
      \code{ModuleHasCyclicDependency} & \pct{0.09} \\
      \code{CannotExtendTable} & \pct{0.09} \\
      \code{OccursCheckFailed} & \pct{0.09} \\
      \code{TypesAreUnrelated} & \pct{0.09} \\
    \end{tabular}
  \end{tabular}
\end{table}

@@

  \item
    Two errors that appear in the \mstrict{} records
    never appear in \mnonstrict{}: \code{OccursCheckFailed} and \code{IncorrectGenericParamCount}.
    We attribute these to more advanced uses of types in \mstrict{} mode.
